\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Carl}
\familyname{\mbox{V. Lewis}}
\title{\small Data Journalist $\star$ Mobile Developer $\star$ Digital Educator}
\phone{+1 (912) 816-7007}
\email{carl@carlvlewis.net}
\homepage{carlvlewis.net}
\social[linkedin]{carlvlewis}
\social[github]{carlvlewis}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% command and color used in this document, independently from moderncv 
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
\renewcommand{\labelitemi}{$\circ$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-1cm}

\section{\textsc{Qualifications summary}}
		\cvitem{\textbullet}{A post-platform journalist}
		\cvitem{\textbullet}{web developer}
		\cvitem{\textbullet}{design thinker}
		\cvitem{\textbullet}{product manager}
		\cvitem{\textbullet}{interaction designer}
		\cvitem{\textbullet}{digital media educator and data visualization developer with more than 7 years of experience in data journalism}
		\cvitem{\textbullet}{news graphics}
		\cvitem{\textbullet}{newsroom interactive storytelling}
		\cvitem{\textbullet}{curriculum design}
		\cvitem{\textbullet}{digital publishing}
		\cvitem{\textbullet}{homepage editing}
		\cvitem{\textbullet}{product management}
		\cvitem{\textbullet}{media entrepreneurship}
		\cvitem{\textbullet}{digital strategy/social media management}
		\cvitem{\textbullet}{mobile front-end design/development}
		\cvitem{\textbullet}{interaction programming and Wordpress/Drupal content management development.}

\section{\textsc{Technical Skills}}
		\cvitem{\textbullet}{\textbf{Web Development}: HTML5, CSS3, Javascript, Python-Django, d3.js, WordPress/Drupal development, Twitter Bootstrap, Ruby on Rails, Git workflow, Markdown, jQuery, CartoDB, Leaflet.js, Curriculum Design}
		\cvitem{\textbullet}{\textbf{Digital Media}: Digital Media Business Models, Hacking the news, iPhoneography/mobile reporting, Multimedia/real-time reporting., Interactive storytelling., MapBox Studio-Open Street Maps, News metrics and analytics, Content marketing for newsrooms, Digital audience acquisition and retention strategies, Deadline daily news writing and reporting, Data visualization under deadline, Journalism in all formats (post-platform), R, Educational technology., Syllabus/curriculum preparation and delivery., Data Visualization, Google tools (viz. playground, fusion tables, Refine, etc.), Documentation writing}


\section{\textsc{Professional Experience}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
		\cventry{Oct. 2014 - present}{Research Assistant}{Tow Center for Digital Journalism}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Assisting in Tow Center's research endeavors.\item Preparing own research for upcoming report on optimizing data visualization projects for mobile users.	
				\end{itemize}
			}
		}
		\cventry{Aug. 2014 - Sept. 2014}{Data Journalism Consultant}{Vocativ}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Invited to serve as one-month, in-house training consultant for Vocativ.com's rapidly expanding Manhattan newsroom, primarily teaching reporters how to incorporate and visualize data in their stories in a way that sheds a new light on the story for users.	
				\end{itemize}
			}
		}
		\cventry{Jun. 2013 - present}{Adjunct instructor, faculty news organization advisor}{Center for Collaborative Journalism at Mercer University}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Teach courses on JavaScript, HTML and CSS basics, mobile development best-practices, real-time reporting, data journalism and visual storytelling\item Serve alongside faculty, journalists and media professionals as an instructor for annual Camp CCJ for digital media students at Center for Collaborative Journalism.\item Spoken on panels with editors and professors, including - How is Journalism Different in the Digital Age? , - Social Media for Journalists, - Building a Brand as a Journalist  and  - Mobile App Development with Little-to-No Programming Experience.\item Led lightning talks on topics including -Making the Business of Digital Journalism Work, -Audience and Metrics and -Wireframing, Prototyping and UX. -Serve as advisor for student news organization, The Cluster, leading quarterly workshops and remotely helping fix problems as they may arise on mercercluster.com. Oversaw 2014 redesign of site.	
				\end{itemize}
			}
		}
		\cventry{March 2003 - present}{Co-Founder}{Borrow.ly}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Upon receiving a \$5,000 exploratory grant from The Collaborative Fund in early 2014, my business partner and I set out to build the product I long believed could help shift decades of audience and revenue loss at daily newspapers from the once-lucrative classified advertising section, revenue which was swiftly poached by P2P exchanges such as Craigslist and eBay.\item We built the product using the Ruby on Rails programming language, and it received widespread acclaim and a loyal local audience in our initial target market in Fort Greene, Brooklyn.-Briefly named : one of Silicon Alley's hottest civic-tech startups by StartupBoost.\item Unforeseen circumstances, including the death of my mother and my business partner's acceptance of a full-time offer at Google, shelved the project for the time being.	
				\end{itemize}
			}
		}
		\cventry{April 2014 - July 2014}{Instructor, &quot;Basics of Modern Web Design&quot;}{Shuttl.es}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Taught a 12-week micro-learning course via email and in person at the Brooklyn-based TinyLabs, NYC.-Instructed students ranging in age from as young as 15 to as old as 52.\item 5 in-person classes, 20 micro-lessons digitally.	
				\end{itemize}
			}
		}
		\cventry{Jan. 2013 - Feb. 2014}{Newsroom Change Consultant}{Jacksonville Daily-Record}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Developed device-agnostic stylesheet and more user-friendly editorial placement of content.\item Monetized digital presence with local display and inline ads.\item Presented legal, real estate and public notice data in interactive format.\item Implemented integrated print and digital CMS that uses Google Docs as intermediary between InCopy and Wordpress.\item Trained staffers/journalists on new CMS, mobile reporting, social media best practices.	
				\end{itemize}
			}
		}
		\cventry{Aug. 2012 - Jan. 2014}{Digital Media Manager, Online Editor, Social Media Editor}{Savannah Morning News (Morning News Media)}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked as Digital Media Manager in Savannah following the death of my father to be closer to my mom.\item Oversaw content production, digital/social outreach and product development for savannahnow.com, dosavannah.com and other cross-platform company products, achieving a nearly 500 percent growth in social reach and a record 7 million monthly pageviews.\item Managed team of online producers/digital journalists; collaborated with traditional reporters and editors on optimizing print content for digital platforms; worked with marketing and sales departments to bridge the gap between editorial and sales in an ethical manner.\item Developed and executed growth strategies for company-wide social media platforms, including existing accounts on Facebook and Twitter and new accounts on Instagram, Vine, Tumblr and Pinterest to reach younger audiences,\item Increased weekly average social reach from 21,000 to an average of 375,000 by end date. Grew Facebook fans from approximately 8.5K to 24K.\item Introduced "sponsored posts" on dosavannah.com, as well as "sponsored tweets" using retweets from the handle @SMNsponsored.\item Increased Facebook following by more than 115 percent in less than a year. Started new Instagram account that gained 1,400 followers within 7 months.\item Monitored and responded to metrics using Adobe Omniture, Google Analytics, Chartbeat, Parse.ly, Sprout Social and Sparkwise.\item Introduced and trained staffers on new interactive forms of storytelling that allowed producers and reporters to visualize public data with little programming skills.\item Led native app development for iOS and Android platforms. Responsible for 19K app downloads.\item Developed HTML5/responsive content strategies and products, including the June 2013 launch of dosavannnah.com.\item Represented company on Morris Publishing Group's corporate-wide Social Media and Mobile Stategy task-forces\item Redesigned Savannah Morning News Mobile App, causing a threefold increase in active users in two weeks.	
				\end{itemize}
			}
		}
		\cventry{March 2013 - Nov. 2013}{Product Manager, Digital Content Marketer, Front-End Developer}{DoSavannah.com (Morning News Media)}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item As a way to reach younger demographics, our management team at Savannah Morning News decided to expand its arts and culture section into a standalone alt-weekly. I was tasked with building the digital products.\item Developed, designed and launched dosavannah.com and its associated native iOS and Android apps, in addition to my responsibilities as Digital Media Manager.\item Introduced "Sponsored Posts," a native advertising plan that garnered more than \$30,000 in new sponsorship revenue its month-long first sales round.\item Created editorial workflow and trained staffers on using Drupal 7 as a CMS.\item Introduced "The Big Calendar," which quickly became Savannah's top-visited event guide.	
				\end{itemize}
			}
		}
		\cventry{March 2010 - Apr. 2012}{Online Editor}{Exposition Magazine}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Developed website and online publishing system for current affairs magazine at Oxford University using WordPress backend.\item Oversaw online content and site production for expositionmagazine.com, including measuring and reporting site analytics, developing SEO strategies and retooling UX to fit the needs of print redesign. \item Managed digital advertising sales and placement with sponsors Pulse Printing and Oxford Castle.\item Temporarily maintained and managed site from abroad; wrote detailed site documentation for future maintenance.	
				\end{itemize}
			}
		}
		\cventry{Nov. 2010 - Jul. 2012}{Director of Digital Media}{The Cluster \&amp; mercercluster.com}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Founded, developed and launched MercerCluster.com, the online edition of Mercer University's student newspaper, The Cluster.\item Created digital workflow, trained staff in content management, drafted detailed site documentation for future student editors.\item Grew Facebook ‘likes’ from around 30 to more than 900 in less than a month with integrated social media campaign, involving a grassroots contest and non-monetary incentives.	
				\end{itemize}
			}
		}
		\cventry{Jan. 2009 - June 2009}{News Editor, Online Editor}{The Oxford Student}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Produced and edited entire 12-page news section of the University of Oxford’s official student newspaper.- Managed team of 14 reporters and covered more than 40 stories individually.\item Redesigned newspaper website and developed digital workflow. \item Trained staff in content management system. 	
				\end{itemize}
			}
		}
		\cventry{May 2009 - Dec. 2010}{Metro intern, weekend cops reporter}{The Telegraph \&amp; macon.com}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked first as a news reporting intern, then as a weekend beat reporter at Georgia's third-largest daily newspaper.\item Covered general news assignments, as well as local/state politics, crime and education beats.\item Covered more than 110 deadline news stories as an undergraduate.	
				\end{itemize}
			}
		}

\section{\textsc{Other Personal Projects}}
		\cvitem{\textbullet}{Interactive: Savannah-Chatham Restaurant Inspection Database}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked with the Chatham County Health Department, which serves a population of more than 420,000 residents, to integrate county-wide restaurant inspection scores into an XML feed that populates an interactive map produced with CartoDB + Leaflet.js that includes filterable, color-coded markers for each score, allowing users to drill down geographically or filter to see the worst scores.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{The 12 Percent: How People in the Bronx are Coping With the Unemployment Crisis}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Led design, production, project management, narrative and presentation of class-wide project on the unemployment crisis and its effects on the Bronx for The Bronx Ink.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{SavannahNow St. Patrick's Day 2013 Mobile App}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Managed all aspects of project development for Savannah Morning News' mobile app for the 137th Annual St. Patrick's Day Parade and Festival, the second-largest annual St. Patrick's gathering the nation. Success of app, reaching nearly 10,000 downloads, drove savannahnow.com to reach record unique visitors and pageviews.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{Storm Guide by savannahnow.com and Georgia Power}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item For the 2013 hurricane season, I built a native iOS and Android app with an accompanying HTML5 mobile site to tie in with the print edition of our annual “Hurricane Guide” sponsored by Georgia Power. Sponsorship netted \$30,000 in new revenue for company.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{Interactive: Who are the biggest polluters in Georgia – and why?}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked alongside SMN environmental reporter Mary Landers to distill EPA data into meaningful metrics, using the resulting benchmarks to produce an interactive bubble map, charts and table of the states's worst offenders.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{Interactive: Chatham County Commission Payments Vary Widely. But why?}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked alongside SMN county government reporter Eric Curl to take county spending data and break down the logical gaps and holes, which later resulted in a three-part investigative series on the county's inaccurate budgeting habits.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}

\section{\textsc{Education}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2012}{Master, Digital Media}{Columbia University Graduate School of Journalism}{}{GPA:  }{}
\cventry{2011}{Bachelor, Journalism,Southern Studies, Honors.}{Mercer University}{}{GPA: 3.94}{}
\cventry{2010}{College, St. Peter&#39;s College International Studies Course}{University of Oxford, St. Peter&#39;s College}{}{GPA:  }{}






\section{\textsc{Publications}}
		\cvitem{\textbullet}{Lewis, Carl V., \textit{\href{}{Big Data, Small Screens: Displaying Complex, Multivariate Datasets on Mobile – and Does Consumer Mobile Usage Indicate a Positive ROI? Forthcoming from the Tow Center for Digital Journalism.}} }
		\cvitem{\textbullet}{Lewis, Carl V., \textit{\href{}{Transcending the &#39;Editorial Thunder&#39;: Atlanta&#39;s Newspaper Coverage of the 1960 Student Lunch-Counter Sit-ins.}} The Spires. Mercer University Press; Macon, Ga., 2011. }
		\cvitem{\textbullet}{Lewis, Carl V., \textit{\href{}{The Newspaper that Fell From its Ivory Tower: Why the Internet isn&#39;t to Blame for the Decline of The Philadelphia Inquirer.}} May 2012}


\section{\textsc{Extra Curricular Awards}}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}
		\cvitem{\textbullet}{#<Mustache:0x007f89b2ae7688>}

\end{document}
%% end of file `page.tex'.
